---
title: "backend-calculator"
author: "Beck Addison"
date: "11/2/2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
#region-con <- read_csv("Files/data/euc-m.csv")
```

```{r import-data-packages}
library(tidyverse)
library(shiny)
library(readxl)
```

```

```
   region-con <- read.xlsx(
      paste(
      "Files/data/euc-",
      substr(input$what-region,1,1),
      ".xlsx",
      sep =""),
      sheetName = "Btu")
    
    region-exp <-  read.xlsx(
      paste(
      "Files/data/eue-",
       substr(input$what-region,1,1),
       ".xlsx",
      sep =""),
      sheetName = "dollars")
```

Do you have solar, if so how mcuh in kwh 
What kind of water heater (gas, electric, hybrid electric, solar)
What kind of heating (electic, gas)
What kind of lighting (LED vs Incandescent)
What kind of car (Electric vs ICE)

```{r calculators}
environ-calc <- function(region, subregion, urban, climate, housingtype, sqft, rent, yearcst, hshld, income, included_in_rent, heating_fuel) {
  
}

##Calculates the overall p
calc_pricept <- function(gas_items, elec_items) {
  gasoline_car = TRUE
  
  return (0.20*gas_items+0.15*elec_items)/2
}

calc_num <- function(items) {
  
}

pointarrbaseline <- c();
pointarrimproved <- c();


fin-calc <- function(userSalary, currEn, pricePt, year) {
  while (year <= 2050) {
    point = userSalary - (pricePt*currEn)*0.15*year/10 
    
    pointarrbaseline.append(point)
    
    pricePt = pricePt*0.15*year/10
  }
}


```

You can also embed plots, for example:

```{r shiny-io, echo=TRUE}
ui <- fluidPage(
  titlePanel("Test Page"),
  sidebarLayout(
    sidebarPanel(
      numericInput("salary", 
                   
                   label = "What is your annual estimated salary?",
                   value = 50000,
                   min = 10000,
                   max = 900000,
                   step = 5000),
      
      selectInput("want-to-spend", 
                   
                  label = "What percentage of your income
                   do you see yourself comfortably spending?", 
                   
                  choices = c(
                     "5 percent",
                     "10 percent",
                     "15 percent",
                     "25 percent",
                     "I'm all in! (up to 75 percent)"
                     )
                  
                   ), 
      selectInput("what-region", 
                  label = "In what region of the U.S. do you currently
                  live?",
                  choices = c("Northeast","Midwest","South","West")
                  ),
      selectInput("what-car",
                  label = "Do you have a car? If so, gasoline, electric
                  or hybrid",
                  choices = c(
                    "No car", "Gasoline", "Electric","Hybrid","solar")),
      selectInput("what-heater",
                  label = "Do you have an electric water heater, or gas?",
                  choices = c("Electric", "Gas","Hybrid")),
      selectInput("what-lighting",
                  label = "What kind of lights do you have, for the most part?",
                  choices = c("Incandescent","LED")),
                  )
      ),
    
  mainPanel(
    plotOutput("finance_plot"),
    textOutput("info"),
    tags$a(
      href = "https://www.eia.gov/consumption/residential/index.php",
      "Source: EIA",
      target = "_blank"
      )
  )
)
server <- function(input, output) {
  
 # us_con <- read_xlsx("Files/data/euc-us.xlsx", sheet = "Btu", range = "A")
  
 # us_exp <- read_xlsx("Files/data/eue-us.xlsx", sheet = "dollars", range = "A4:N93", col_names = TRUE, .name_repair = "unique") %>%
 # pivot_longer(cols = -"...1", names_to = '...1')
  
  output$finance_plot <- renderPlot({
    calc_pricept("what")
    color = "black"
    ggplot(test_tibble, aes(x = random_times, y = random_nums)) +
      geom_point()
  })

}

shinyApp(ui = ui, server = server)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
